---
title: "Data_Sources"
author: "Jason Bernheimer"
date: "2/1/2021"
output: html_document
---

``` {r}
library(ggplot2)
library(ggvis)
library(ggthemes)
library(RColorBrewer)
library(scales)
library(readr)
library(skimr)
library(janitor)
library(forcats)
library(tidyr)
library(lubridate)
library(stringr)
library(assertive.types)
library(assertive)
library(visdat)
library(fuzzyjoin)
library(stringdist)
library(reclin)
library(dplyr)
# Data
library(OECD)
```

## OECD Data

```{r}
OECD::search_dataset("Health")
```

```{r eval=FALSE, include=TRUE}
# this is to get the data from OECD and save it to the directory
# dont run this code unless there are issues with the data

#     df <- OECD::get_dataset("HEALTH_REAC")
#     save(df, file = "healthdata.Rdata")

#     df2 <- OECD::get_dataset("SHA", start_time = 2017, end_time = 2017)
#     save(df2, file = "healthcosts.Rdata")
```

```{r}
# load data since it has already been saved in the project directory

load("healthdata.Rdata")

load("healthcosts.Rdata")

# head(df, 10)
```

```{r eval=FALSE, include=FALSE}
# Data Definitions
OECD::get_data_structure("HEALTH_REAC")

key <- get_data_structure("HEALTH_REAC")

key_VAR <- key[["VAR"]]
key_UNIT <- key[["UNIT"]]
```


Ignore this chunk:
```{r eval=FALSE, include=FALSE}
# USE ALL OECD COUNTRIES FOR NOW
# countries <- unique(df$COU)
# 
# COU_exclude <- c("AUS", "CAN", "ISR", "JPN", "KOR", "MEX", "NZL", "USA", "BRA", "CHL", "CHN", "IND", "IDN", "RUS", "ZAF", "COL", "CRI")
```

```{r eval=FALSE, include=FALSE}
# select only 2019 for ease of use for now
mydata <- df %>%
  filter(obsTime == 2019)

# GPs
mydata %>%
  filter(VAR == "EMPLGENE" |VAR == "EMPLGENP"|VAR ==  "EMPLOTGP") %>%
  filter(UNIT == "PERSMYNB" | UNIT == "PERMEDNB")
key_UNIT %>%
  filter(id == c("PERSMYNB", "PERMEDNB"))

# Specialists
mydata %>%
  filter(VAR == "EMPLSPMP" |VAR == "EMPLGENP"|VAR ==  "EMPLOTGP") %>%
  filter(UNIT == "PERSMYNB" | UNIT == "PERMEDNB")

```


Things to note about Physicians: 

* `VAR` = `EMPLGENE`
  + this is all that is needed because it is the combined general practitioners and will mitigate slight differences in deffinitions between the two sub categories `EMPLGENP` & `EMPLOTGP` or which `EMPLGENE` is the sum of the two.
* `UNIT`
  + `PERSMYNB` - Number of persons (head counts)
  + `PERMEDNB` - % of physicians (head counts)
    + this is impacted by `EMPLOTPH` so I will have to calculate my own percentages between **specified** GPs and Specialists rather than all doctors.

`VAR`:

* `EMPLOTPH` - Medical doctors not further defined

**are paediatricians specialists?** They are defined as specialists in the data but maybe we should change that? - if we did, we would have to remove CRI (Costa Rica) because they dont have that data.


```{r eval=FALSE, include=FALSE}
temp <- df %>%
  filter(obsTime == 2015) 

temp <- mutate(temp, COU = as.factor(COU))

levels(temp$COU)
```

Years 2015, 2016, & 2017 all have 43 of the 44 countries total. 

2017 is missing the *Czech Republic* and *Finland*, be sure to exclude *Russia*, *Indonesia*, and *South Africa* because they don't have full data.


Now that I understand the data, let's make something actually useful:

## Real Code

**Health care employment data**

```{r}
doctors <- df %>%
  filter(obsTime == "2017") %>%
  dplyr::select(-TIME_FORMAT)

countries_keep <- c("AUS", "AUT", "BEL", "CAN", "CHE", "CHL", "DEU", "DNK", "ESP", "EST", "FRA", "GBR", "GRC", "HUN", "IRL", "ISL", "ISR", "ITA", "KOR", "LTU", "LUX", "LVA", "MEX", "NLD", "NOR", "NZL", "POL", "PRT", "SVN", "SWE", "TUR", "USA")

doctors <- doctors %>%
  filter(COU %in% countries_keep)
```


```{r}
doctors <- doctors %>%
  filter(UNIT == "PERSMYNB")
  
doctors <- doctors %>%
  filter(VAR == "EMPLGENE" | VAR == "EMPLSPMP") %>%
  dplyr::select(-UNIT, -OBS_STATUS) %>%
  spread(VAR, obsValue)

doctors <- doctors %>%
  rename(total_GPs = EMPLGENE, total_SPs = EMPLSPMP)

doctors <- doctors %>%
  mutate(pct_GP = total_GPs / (total_GPs + total_SPs))
```


**Health care cost data**

```{r}
key2 <- get_data_structure("SHA")
```

```{r}
costs <- df2 %>%
  dplyr::select(-TIME_FORMAT)

costs <- costs %>%
  filter(LOCATION %in% countries_keep)

costs <- costs %>%
  filter(HP == "HPTOT" & HF == "HFTOT" & HC == "HCTOT")

costs <- costs %>%
  filter(MEASURE == "PARPIB" | MEASURE == "VRPPPR") %>%
  dplyr::select(MEASURE, COU = LOCATION, obsTime, obsValue) %>%
  spread(MEASURE, obsValue) %>%
  rename(pct_GDP = PARPIB, per_capita = VRPPPR)
```

Measures:

* PARPIB - % of GDP
* VRPPPR - Per capita, constant prices, constant PPPs, OECD base year

HF, HP, & HC should all be "__TOT" but for some reason that's not working like it does in the excel...

Figured out the issue: r only allowed for 1,000,000 obs. in df2 so I had to filter out the correct year as I originally loaded it.





