---
title: "Data_Sources"
author: "Jason Bernheimer"
date: "2/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## OECD Data

```{r}
library(OECD)
df <- OECD::get_dataset("HEALTH_REAC")
head(df, 10)
```

```{r}
unique(df$COU)
```




## Eurostat

```{r}
library(eurostat)
```

What functions are in the Eurostat package?

| Function | Explanation |
|----|--------------|
|add_nuts_level|Add the statistical aggregation level to data frame|
|check_access_to_data | Check access to ec.europe.eu|
|clean_eurostat_cache | Clean Eurostat Cache|
|cut_to_classes | Cuts the Values Column into Classes and Polishes the Labels|
|dic_order | Order of Variable Levels from Eurostat Dictionary.|
|eu_countries | Countries and Country Codes|
|eurostat_geodata_60_2016| Geospatial data of Europe from Gisco in 1:60 million scale from year 2016|
|eurostat-package  | R Tools for Eurostat open data|
|eurotime2date  | Date Conversion from Eurostat Time Format|
|eurotime2num  |Conversion of Eurostat Time Format to Numeric|
|get_bibentry | Create A Data Bibliography|
|get_eurostat  |Read Eurostat Data|
|get_eurostat_dic  | Download Eurostat Dictionary|
|get_eurostat_geospatial | Download Geospatial Data from GISCO|
|get_eurostat_json| Get Data from Eurostat API in JSON|
|get_eurostat_raw  |Download Data from Eurostat Database|
|get_eurostat_toc |Download Table of Contents of Eurostat Data Sets|
|harmonize_country_code| Harmonize Country Code|
|harmonize_geo_code |Harmonize NUTS region codes that changed with the 'NUTS2016' definition|
|label_eurostat |Get Eurostat Codes|
|nuts_correspondence| Correspondence Table NUTS2013-NUTS2016|
|recode_to_nuts_2013 |Recode geo labels and rename regions from NUTS2016 to NUTS2013|
|recode_to_nuts_2016 |Recode geo labels and rename regions from NUTS2013 to NUTS2016|
|regional_changes_2016 |Changes in regional boundaries NUTS2013-NUTS2016|
|search_eurostat| Grep Datasets Titles from Eurostat|
|tgs00026| Auxiliary Data|

```{r}
toc <- get_eurostat_toc()

toc
```

```{r}

```


Indicators: 
HIHSI062004 - Current health care expenditure by all financing agents (total), as percentage of GDP 
HIHSI062005 - Current health care expenditure by public sector, as percentage of GDP 
HIHSI062007 - Current health care expenditure by household out-of-pocket payment, as percentage of GDP 
HIHSI062008 - Current health care expenditure by voluntary health care payment schemes, as percentage of GDP 
HIHSI063004 - Current health care expenditure by all financing agents, in millions of PPS 
HIHSI063005 - Current health care expenditure by public sector, in millions of PPS 
HIHSI063007 - Current health care expenditure by household out-of-pocket payment, in millions of PPS 
HIHSI063008 - Current health care expenditure by voluntary health care payment schemes, in millions of PPS 

